---
title: "Support Cases Project"
author: "Thomas Sato"
date: "5 June 2023 - 22 June 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Importing packages
```{r, message = FALSE}
library(readxl)
library(tidyverse)
library(tidytext)
```

Reading in the data
```{r}
SupportCases <- read_excel("All Support Cases 6-2-2023 Support Project.xlsx")
```

# Number of Support Cases per Product

Filling in missing product data from the case title.
```{r}
caselist <- SupportCases$`Case Title`
productcaseids <- str_match(caselist, "\\d{3}") # Matches first three digits in string
sum(is.na(productcaseids))
```

There are 934 values in the Case Title field that do not have three consecutive numbers.

Creating a data frame that consists of each of the products and the corresponding number
```{r}
productdf <- tibble(unique(SupportCases$Product))
productdf <- productdf %>%
  mutate(num = str_match(`unique(SupportCases$Product)`, "\\d{3}"))

# Removing unnecessary duplicates and changing strings by hand.
# This is in order to prevent a many-to-many relationship when joining the tables together.
productdf <- productdf[-c(19, 21, 29, 30, 1, 22, 32, 23), ]
productdf[6, 2] <- "751 Avocado"
productdf[20, 2] <- "751 Melon"
productdf[11, 2] <- "751 Kiwi"
productdf[19, 2] <- "751 Mango"
productdf[21, 2] <- "901B"
productdf[22, 2] <- "901R"
productdf[23, 2] <- "901D"
productdf[7, 2] <- "901S"
colnames(productdf)[1] <- "Product"
```

Modifying the dataset to fill in the Product column with the values from the case title.  There is probably a more efficient way to do this.
```{r, message = FALSE}
SupportCases <- SupportCases %>%
  mutate(caseids = productcaseids) %>%
  left_join(productdf) %>%
  mutate(caseids = ifelse(is.na(caseids), num, caseids)) %>%
  left_join(productdf, by = c("caseids" = "num")) %>%
  select(-Product.x, -num, Product.y) %>%
  select(caseids, Product.y, everything())

# 944 missing values in the Product column after joining
sum(is.na(SupportCases$Product.y))
```

Additional text cleaning just so things look a little cleaner
```{r}
SupportCases$Product.y <- ifelse(SupportCases$Product.y == "F-751MAN Mango Quality Meter", "F-751 Mango Quality Meter", SupportCases$Product.y)
SupportCases$Product.y <- ifelse(SupportCases$Product.y == "GasD 8000 Portable Gas Detector - Formaldehyde - 8160-20.00m1", "GasD 8000 Portable Gas Detector", SupportCases$Product.y)
```

Adding a flag for the RMAs
```{r}
# Creating the flag column
RMAflag <- apply(SupportCases, 1, function(row){
  any(grepl("RMA", row))
})

# Binding to the original dataset
SupportCases <- SupportCases %>%
  mutate(RMA = RMAflag) %>%
  select(RMA, everything())

sum(SupportCases$RMA)
```
There are 699 RMA Support Cases in the dataset.

(Aside): Converting the matrix column of case IDs to a vector in order to export the dataset
```{r}
SupportCases <- SupportCases %>%
  mutate(caseids = as.vector(caseids))
```

# Content Analysis

Removing observations that have no description.
```{r}
SupportCasesDescriptions <- filter(SupportCases, !is.na(Description)) %>%
  select(Description, `Case Title`, Product.y, everything())
```

Unnesting tokens in the description
```{r}
descriptionstokens <- unnest_tokens(SupportCasesDescriptions, word, Description)

# Looking at most common words over the whole dataset
mostcommonwords <- descriptionstokens %>%
  group_by(word) %>%
  summarize(n = n()) %>%
  arrange(desc(n))
```

Creating a function that takes in the name of a product (as defined in "prodlist"), and returning a dataset of the most common words in the descriptions of that particular product.
```{r, message = FALSE}
productmostcommonwords <- descriptionstokens %>%
  group_by(Product.y, word) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) %>%
  arrange(Product.y)

product_words <- function(product) {
  
  prodmostcommon <- productmostcommonwords %>%
    filter(Product.y == product)
  
  return(prodmostcommon)
  
}
```

```{r}
prodlist <- unique(productmostcommonwords$Product.y)
prodlist

# Twenty most common words for the F-751 Avocado Quality Meter
head(product_words(prodlist[10]), n = 20)
```

Finding the most common word for each individual description
```{r, message = FALSE}
descriptionmostcommon <- descriptionstokens %>%
  group_by(`Case Number`, word) %>%
  summarize(n = n()) %>%
  group_by(`Case Number`) %>%
  filter(n == max(n)) %>% # Multiple rows for each case
  group_by(`Case Number`) %>%
  mutate(word = paste0(word, collapse = ", ")) %>%
  distinct()

# Joining to the filtered dataset.
SupportCasesDescriptions <- left_join(SupportCasesDescriptions, descriptionmostcommon) %>%
  select(Description, word, n, everything())
```



# Visualizations of Support Cases

There are many missing values in the data in terms of the product, but otherwise this is the number of cases for every product.
```{r}
ggplot(SupportCases, aes(fct_rev(fct_infreq(Product.y)))) +
  geom_bar(fill = "blue", color = "black") +
  coord_flip() +
  labs(x = "Product", y = "Number of Cases", title = "Number of Cases per Product") +
  theme_bw() +
  geom_text(aes(label = ..count..), stat = "count", hjust = -0.15) +
  scale_y_continuous(limit = c(0, 1000))
```

Filtering out missing values for the graph.
```{r}
SupportCases %>%
  filter(!is.na(Product.y)) %>%
  ggplot(aes(fct_rev(fct_infreq(Product.y)))) +
    geom_bar(fill = "blue", color = "black") +
    coord_flip() +
    labs(x = "Product", y = "Number of Cases", title = "Number of Cases per Product") +
    theme_bw() +
    geom_text(aes(label = ..count..), stat = "count", hjust = -0.15) +
    scale_y_continuous(limit = c(0, 400))
```

# Time Taken to Resolve Issues

Creating a column for the difference in time in days for when the case was created and when it was resolved
```{r}
SupportCases <- SupportCases %>%
  mutate(TimeUntilResolution = as.numeric(difftime(`Resolution Date`, `Created On`), units = "days")) %>%
  select(TimeUntilResolution, everything())

# Five number summary for the time until resolution
summary(SupportCases$TimeUntilResolution)
```

```{r}
ggplot(SupportCases) +
  geom_histogram(aes(TimeUntilResolution), binwidth = 10, fill = "orange", color = "black") +
  labs(x = "Time Until Resolution (Days)", y = "Frequency", title = "Distribution of Time Until Resolution for Support Cases") +
  theme_bw()
```

Upon first glance, the distribution seems very right-skewed, with some outliers.

```{r}
boxplot.stats(SupportCases$TimeUntilResolution)$out # List of all outliers in the data

# Finding outliers using IQR Criterion
outlying_indices <- which(SupportCases$TimeUntilResolution %in% boxplot.stats(SupportCases$TimeUntilResolution)$out)

outlying_indices

# Filtering out outliers
support_outliers <- SupportCases[-c(outlying_indices), ]

ggplot(support_outliers) +
  geom_histogram(aes(TimeUntilResolution), binwidth = 1, fill = "orange", color = "black") +
  labs(x = "Time Until Resolution (Days)", y = "Frequency", title = "Distribution of Time Until Resolution for Support Cases", caption = "Filtered for Outliers") +
  theme_bw()
```

Using a binwidth of one day, it is easy to see that there is modality, where most problems are resolved within a day.  The distribution is still very clearly right skewed as well.

# Time Until Resolution by Product

Making an average time until resolution for each product
```{r}
resolutiontime <- SupportCases %>%
  group_by(Product.y) %>%
  summarize(avgtime = mean(TimeUntilResolution, na.rm = TRUE))

# Removing NAs and NaNs
resolutiontime <- na.omit(resolutiontime)
```

There are 99 cases that have a time difference that is less than zero.
```{r}
nrow(SupportCases %>% filter(TimeUntilResolution <= 0))
```

Graph of time until resolution, but filtering out those observations that have a time difference less than zero.
```{r}
resolutiontimezero <- SupportCases %>%
  filter(TimeUntilResolution > 0) %>%
  group_by(Product.y) %>%
  summarize(avgtime = mean(TimeUntilResolution, na.rm = TRUE))

# Removing NAs and NaNs
resolutiontimezero <- na.omit(resolutiontimezero)
```

```{r}
ggplot(resolutiontimezero, aes(fct_reorder(Product.y, avgtime), avgtime)) +
  geom_col(fill = "darkgoldenrod4", color = "black") +
  coord_flip() +
  labs(x = "Product", y = "Average Time Until Resolution (Days)", title = "Average Resolution Time by Product", caption = "Filtered for time differences < 0") +
  theme_bw() +
  geom_text(aes(label = round(avgtime)), hjust = -0.1) +
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, by = 10))
```

The result is very similar, since the zero values do not affect the mean very heavily.

# RMAs

```{r, message = FALSE}
RMAratios <- SupportCases %>%
  group_by(Product.y, RMA) %>%
  summarize(n = n()) %>%
  pivot_wider(names_from = RMA, values_from = n) %>%
  mutate(`TRUE` = ifelse(is.na(`TRUE`), 0, `TRUE`),
         RMAratio = `TRUE` / (`TRUE` + `FALSE`))
```

Graph of the ratio of RMA cases by product
```{r}
ggplot(RMAratios, aes(fct_reorder(Product.y, RMAratio), RMAratio)) +
  geom_col(fill = "violet", color = "black") +
  coord_flip() +
  theme_bw() +
  labs(x = "Product", y = "Ratio of Cases that were RMAs", title = "Ratio of RMA by Product") +
  geom_text(aes(label = sprintf(RMAratio, fmt = "%#.2f")), hjust = -0.1) +
  scale_y_continuous(limits = c(0, 0.6), breaks = seq(0, 0.6, by = 0.1))
```

# Looking at support cases with categories

Reading in the data
```{r, warning = FALSE}
SupportCasesCategories <- read_excel("SupportCasesDescriptionswithCategory1.xlsx")
```


Creating the visualization for category of support case by product.
```{r}
ProductCategories <- function(product, ds = SupportCasesCategories, fillcolor = "red3", na.rm = FALSE) {
  # Takes in ds as a keyword argument when I want see categories for different datasets
  # Removing category NAs as another keyword argument for certain datasets
  
  if(na.rm) {
    ds <- ds %>%
      filter(!is.na(Category))
  }
  
  ds <- ds %>%
    filter(Product.y == product) %>%
    group_by(Category) %>%
    summarize(n = n()) %>%
    arrange(desc(n)) %>%
    head(n = 10)
  
  categoryplot <- ggplot(ds) +
    geom_col(aes(fct_reorder(Category, n), n), fill = fillcolor, color = "black") +
    coord_flip() +
    theme_bw() +
    labs(x = "Category",
         y = "Number of Cases",
         title = paste("Categories for", product)) +
    geom_text(aes(x = fct_reorder(Category, n), y = n, label = n), hjust = -0.4) +
    scale_y_continuous(limits = c(0, max(ds$n, na.rm = T) + ceiling(max(ds$n, na.rm = T) * 0.05)))
  
  return(categoryplot)
    
}
```

```{r}
# Quick text cleaning
SupportCasesCategories$Product.y <- ifelse(SupportCasesCategories$Product.y == "F-751 Kiwifruit Quality Meter", "F-751 Kiwi Quality Meter", SupportCasesCategories$Product.y)
SupportCasesCategories$Product.y <- ifelse(SupportCasesCategories$Product.y == "CI-710s SpectraVue Leaf Spectrometer", "CI-710S SpectraVue Leaf Spectrometer", SupportCasesCategories$Product.y)
SupportCases$Product.y <- ifelse(SupportCases$Product.y == "CI-710s SpectraVue Leaf Spectrometer", "CI-710S SpectraVue Leaf Spectrometer", SupportCases$Product.y)

# Making it easier to see and input each product into the function
products <- unique(SupportCasesCategories$Product.y)
products
ProductCategories(products[9], na.rm = TRUE)
```

Same type of visualization, but excluding RMAs
```{r}
ProductCategoriesNoRMA <- function(product, ds = SupportCasesCategories) {
  
  ds <- ds %>%
    filter(Product.y == product & !RMA) %>%
    group_by(Category) %>%
    summarize(n = n()) %>%
    arrange(desc(n)) %>%
    head(n = 10)
  
  categoryplot <- ggplot(ds) +
    geom_col(aes(fct_reorder(Category, n), n), fill = "red2", color = "black") +
    coord_flip() +
    theme_bw() +
    labs(x = "Category",
           y = "Number of Cases",
           title = paste("Categories for", product)) +
    geom_text(aes(x = fct_reorder(Category, n), y = n, label = n), hjust = -0.4) +
    scale_y_continuous(limits = c(0, max(ds$n, na.rm = T) + ceiling(max(ds$n, na.rm = T) * 0.05)))
  
  return(categoryplot)
    
}
```

```{r}
ProductCategoriesNoRMA(products[5])
```

It doesn't seem like the RMAs being present or not will affect the data that much.  When filtering out the descriptions with missing values, the number of RMAs decreases significantly.  Especially if the RMA belongs to a category that does not have very many cases, the visualization will not change much, if at all.
```{r}
sum(SupportCases$RMA)
sum(SupportCasesCategories$RMA)
```

Joining together the categories to the original SupportCases dataset.
```{r, message = FALSE}
SupportCases <- SupportCases %>%
  left_join(select(SupportCasesCategories, Category, `Case Number`)) %>%
  select(Category, Description, everything())
```

Filtering for resolution date gives different number of rows than filtering for Status being "Resolved", interestingly.
```{r}
SupportCasesResolvedWithoutRMA <- SupportCases %>%
  filter(RMA == FALSE & Status == "Resolved")

nrow(SupportCasesResolvedWithoutRMA)
nrow(SupportCases %>% filter(RMA == FALSE & !is.na(`Resolution Date`)))
```

## Support cases with resolutions and no RMAs

```{r}
ProductCategories(products[9], SupportCasesResolvedWithoutRMA, na.rm = TRUE)
```


```{r}
resolutiontimecategories <- SupportCases %>%
  filter(!is.na(Category) & !is.na(TimeUntilResolution))

nrow(resolutiontimecategories)
nrow(SupportCases %>% filter(!is.na(TimeUntilResolution)))
```
There are only 552 cases in which there is a category, and also a difference in time.  There are 1,238 cases that have no resolution date in the whole dataset.  There are 2,887 observations in the whole dataset.

```{r}
resolutiontimecategories %>%
  group_by(Category) %>%
  summarize(n = n(), avgtime = mean(TimeUntilResolution)) %>%
  arrange(desc(avgtime)) %>%
  head(n = 20) %>%
  ggplot(aes(fct_reorder(Category, avgtime), avgtime)) +
    geom_col(fill = "yellow", color = "black") +
    coord_flip() +
    labs(x = "Category", y = "Average Time Until Resolution (Days)", title = "Average Time Until Resolution by Category of Case") +
    theme_bw() +
    geom_text(aes(label = round(avgtime), hjust = -0.2)) +
    geom_text(aes(y = 0, label = n), hjust = 1.15) +
    scale_y_continuous(limits = c(0, 550), breaks = seq(0, 550, by = 100))
```

Important to note with this visualization:  This is made with 552 / 2887 = 19.1 % of the overall data, which is the data that has both a category, and a resolution date.  Also, the high number of days in terms of average time may be due to some categories only having one observation, that observation being one that has a high time until resolution.

The numbers to the left of the bars indicate the number of cases associated with each category, i.e. there were 4 cases that were categorized as "Unknown" and on average for those 4 cases, it took 158 days to resolve.

This visualization is the same as before, but filtered for more than 5 observations for each category.  So the categories with 5 or fewer cases attributed to them are taken out.
```{r}
resolutiontimecategories %>%
  group_by(Category) %>%
  summarize(n = n(), avgtime = mean(TimeUntilResolution)) %>%
  filter(n > 5) %>% # Filtering for more than 5 observations
  arrange(desc(avgtime)) %>%
  head(n = 20) %>%
  ggplot(aes(fct_reorder(Category, avgtime), avgtime)) +
    geom_col(fill = "yellow2", color = "black") +
    coord_flip() +
    labs(x = "Category", y = "Average Time Until Resolution (Days)", title = "Average Time Until Resolution by Category of Case", caption = "Filtered for > 5 observations per category") +
    theme_bw() +
    geom_text(aes(label = round(avgtime), hjust = -0.2)) +
    geom_text(aes(y = 0, label = n), hjust = 1.15) +
    scale_y_continuous(limits = c(0, 70), breaks = seq(0, 70, by = 10))
```

Now I wanted to filter for RMAs, and see how long it took to solve certain issues given it was not an RMA.
```{r}
resolutiontimecategories %>%
  filter(!RMA) %>%
  group_by(Category) %>%
  summarize(n = n(), avgtime = mean(TimeUntilResolution)) %>%
  filter(n > 5) %>% # Filtering for more than 5 observations
  arrange(desc(avgtime)) %>%
  head(n = 20) %>%
  ggplot(aes(fct_reorder(Category, avgtime), avgtime)) +
    geom_col(fill = "yellow3", color = "black") +
    coord_flip() +
    labs(x = "Category", y = "Average Time Until Resolution (Days)", title = "Average Time Until Resolution by Category of Case", caption = "Filtered for > 5 observations per category", subtitle = "No RMAs Included") +
    theme_bw() +
    geom_text(aes(label = round(avgtime), hjust = -0.2)) +
    geom_text(aes(y = 0, label = n), hjust = 1.15) +
    scale_y_continuous(limits = c(0, 70), breaks = seq(0, 70, by = 10))
```


# Saving all visualizations

Overall support cases
```{r, eval = FALSE}
for(i in products) {
  ggsave(filename = paste(i, "Support Case Categories", ".png"),
         plot = ProductCategories(i, SupportCasesCategories, na.rm = TRUE, fillcolor = "green"),
         path = paste(getwd(), "\\Visualizations", sep = ""),
         width = 10,
         height = 5)
}
```


Categories for cases that were resolved without RMAs.
```{r, eval = FALSE}
for(i in products) {
  ggsave(filename = paste(i, "Resolved No RMA", ".png"),
         plot = ProductCategories(i, SupportCasesResolvedWithoutRMA, na.rm = TRUE, fillcolor = "blue"),
         path = paste(getwd(), "\\Visualizations", sep = ""),
         width = 10,
         height = 5)
}
```


